---
title: "lab1"
author: "Miker"
date: "2021/9/16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# part1
**1. Generate 200 random values from the standard exponential distribution and store them in a vector exp.draws.1. Find the mean and standard deviation of exp.draws.1.**
```{r}
exp.draws.1<-rexp(n=200)
mean(exp.draws.1)
sd(exp.draws.1)
```

  **2.Repeat, but change the rate to 0.1, 0.5, 5 and 10, storing the results in vectors called exp.draws.0.1, exp.draws.0.5, exp.draws.5 and exp.draws.10.**
```{r}
exp.draws.0.1<-rexp(n=200,rate = 0.1)
exp.draws.0.5<-rexp(n=200,rate = 0.5)
exp.draws.5<-rexp(n=200,rate = 1)
exp.draws.10<-rexp(n=200,rate = 10)
```
  **3. The function plot() is the generic function in R for the visual display of data. hist() is a function that takes in and bins data as a side effect. To use this function, we must first specify what we’d like to plot.**    
  **a. Use the hist() function to produce a histogram of your standard exponential distribution.**
```{r}
hist(exp.draws.1)
```
<br/>**b. Use plot() with this vector to display the random values from your standard distribution in order.**
```{r}
plot(exp.draws.1)
```
<br/>**c. Now, use plot() with two arguments – any two of your other stored random value vectors – to create a scatterplot of the two vectors against each other.**
```{r}
plot(exp.draws.0.1,exp.draws.0.5)
```
<br/>**4. We’d now like to compare the properties of each of our vectors. Begin by creating a vector of the means of each of our five distributions in the order we created them and saving this to a variable name of your choice. Using this and other similar vectors, create the following scatterplots:**
```{r}
means<-c(mean(exp.draws.0.1),mean(exp.draws.0.5),mean(exp.draws.1),mean(exp.draws.5),mean(exp.draws.10))
```
  **a. The five means versus the five rates used to generate the distribution.**
```{r}
rates<-c(0.1,0.5,1,5,10)
plot(rates,means)
```
<br/>**b. The standard deviations versus the rates.**
```{r}
sds<-c(sd(exp.draws.0.1),sd(exp.draws.0.5),sd(exp.draws.1),sd(exp.draws.5),sd(exp.draws.10))
plot(rates,sds)
```
<br/>**c. The means versus the standard deviations. **
```{r}
plot(sds,means)
```
# part2   
**5. R’s capacity for data and computation is large to what was available 10 years ago.**   
**a. To show this, generate 1.1 million numbers from the standard exponential distribution and store them in a vector called big.exp.draws.1. Calculate the mean and standard deviation.**
```{r}
big.exp.draws.1<-rexp(n=1100000)
mean(big.exp.draws.1)
sd(big.exp.draws.1)
```
**b. Plot a histogram of big.exp.draws.1. Does it match the function 1 − e−x? Should it?**
```{r}
hist(big.exp.draws.1)
```
<br/>不符合；不需要，需要符合1-exp(-x)的导数   
**c. Find the mean of all of the entries in big.exp.draws.1 which are strictly greater than 1. You may need to first create a new vector to identify which elements satisfy this.**

**d. Create a matrix, big.exp.draws.1.mat, containing the the values in big.exp.draws.1, with 1100 rows and 1000 columns. Use this matrix as the input to the hist() function and save the result to a variable of your choice. What happens to your data?**

**e. Calculate the mean of the 371st column of big.exp.draws.1.mat.**

**f. Now, find the means of all 1000 columns of big.exp.draws.1.mat simultaneously. Plot the histogram of column means. Explain why its shape does not match the histogram in problem 5b).**

**g. Take the square of each number in big.exp.draws.1, and find the mean of this new vector. Explain this in terms of the mean and standard deviation of big.exp.draws.1. Hint: think carefully about the formula R uses to calculate the standard deviation.**