---
title: "lab1"
author: "Miker"
date: "2021/9/16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# part1
**1. Generate 200 random values from the standard exponential distribution and store them in a vector exp.draws.1. Find the mean and standard deviation of exp.draws.1.**
```{r}
exp.draws.1<-rexp(n=200)
mean(exp.draws.1)
sd(exp.draws.1)
```

  **2.Repeat, but change the rate to 0.1, 0.5, 5 and 10, storing the results in vectors called exp.draws.0.1, exp.draws.0.5, exp.draws.5 and exp.draws.10.**
```{r}
exp.draws.0.1<-rexp(n=200,rate = 0.1)
exp.draws.0.5<-rexp(n=200,rate = 0.5)
exp.draws.5<-rexp(n=200,rate = 1)
exp.draws.10<-rexp(n=200,rate = 10)
```
  **3. The function plot() is the generic function in R for the visual display of data. hist() is a function that takes in and bins data as a side effect. To use this function, we must first specify what we’d like to plot.**    
  **a. Use the hist() function to produce a histogram of your standard exponential distribution.**
```{r}
hist(exp.draws.1)
```
<br/>**b. Use plot() with this vector to display the random values from your standard distribution in order.**
```{r}
plot(exp.draws.1)
```
<br/>**c. Now, use plot() with two arguments – any two of your other stored random value vectors – to create a scatterplot of the two vectors against each other.**
```{r}
plot(exp.draws.0.1,exp.draws.0.5)
```
<br/>**4. We’d now like to compare the properties of each of our vectors. Begin by creating a vector of the means of each of our five distributions in the order we created them and saving this to a variable name of your choice. Using this and other similar vectors, create the following scatterplots:**
  **a. The five means versus the five rates used to generate the distribution.**
  
b. The standard deviations versus the rates.
c. The means versus the standard deviations. **